RQDA package for Qualitative Data Analysis
==========================================
I downloaded the package and installed it from within the standard R64 console.  It asked if I wanted to install Gtk2 and I said OK.  I am getting some errors about Gtk when I  launch RQDA in RStudio about not know my local directory or monitor, but things seem to work.

Text Mining with the tm package
========================================================
To use plotting in tm package I needed to install Rgraphviz from [bioconductor][http://www.bioconductor.org/packages/release/bioc/html/Rgraphviz.html]


```{r}
library("tm")
data("crude")
tdm <- TermDocumentMatrix(crude, control = list (removePunctuation = TRUE,                                                  removeNumbers = TRUE,                                                  stopwords = TRUE))
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(tdm, terms = findFreqTerms(tdm, lowfreq = 6)[1:25], corThreshold = 0.5)
```
Or look for combinations....
```{r}
d<-c("oil","crude","prices")
inspect(DocumentTermMatrix(crude,list(dictionary=d)))
```